Check links on old pages

### 2024-06-28 src/audit-cross-links.Rmd
Updated audit files

```{r setup}
suppressMessages(suppressWarnings(library(glue)))
suppressMessages(suppressWarnings(library(magrittr)))
suppressMessages(suppressWarnings(library(readr)))
suppressMessages(suppressWarnings(library(stringr)))
suppressMessages(suppressWarnings(library(tidyverse)))

load(file="../data/check_new.RData")
load(file="../data/check_old.RData")
```

### create subsets

```{r create}
md %>% 
  filter(miss==0) %>%
  select(yr, fn, stat, base) -> md1

html %>% 
  filter(miss==0) %>%
  mutate(base=fn) %>%
  mutate(html_yr=yr) %>%
  select(base, html_yr) -> html1

match1 <- full_join(md1, html1, by="base")

md %>% 
  filter(miss==0) %>%
  mutate(base=fn) %>%
  mutate(md_yr=yr) %>%
  select(base, md_yr) -> md2

html %>% 
  filter(miss==0) %>%
  mutate(base=link) %>%
  select(fn, yr, base) -> html2

match2 <- full_join(html2, md2, by="base")

```

### mistmatch 1a, new pages that link to non-existent old pages

```{r}
match1 %>% 
  filter(is.na(html_yr))
```

### mistmatch 1b, old pages that link back without recognition

```{r}
match1 %>% 
  filter(is.na(fn))
```

### mistmatch 2a, old pages that link to non-existent new pages

```{r}
match2 %>% 
  filter(is.na(md_yr))
```

### mistmatch 2b, new pages that link back without recognition

```{r}
match2 %>% 
  filter(is.na(fn))
```

>>>>

```{r setup}
verbose <- TRUE
suppressMessages(suppressWarnings(library(glue)))
suppressMessages(suppressWarnings(library(magrittr)))
suppressMessages(suppressWarnings(library(readr)))
suppressMessages(suppressWarnings(library(stringr)))
suppressMessages(suppressWarnings(library(tidyverse)))

load(file="../data/check_new.RData")
n_new <- nrow(new)
load(file="../data/check_old.RData")
n_old <- nrow(old)
size_limit <- 99

inc <- function(x) {
  n <- length(x)
  m <- c(FALSE, x[-1]==x[-n])
  x[m] <- " "
  x
}
test1 <- rep(letters[1:4], 1:4)
test2 <- inc(test1)
data.frame(test1, test2)
```

## pages with no links from new site to old or blog site

```{r no-link-www-1}
new %>% 
  filter(link_miss==1) %>%
  select(dir, page) -> pip1 
msg <- glue(
  "{nrow(pip1)} / {n_new} = {round(100*nrow(pip1)/n_new)}%")
```

### `r msg`

```{r no-lin-www-2}
if (verbose) {
  pip1 %>%
    mutate(dir=inc(dir)) %>%
    head(size_limit)
}
```

### pages with bad links from new site to old site

```{r bad-link-www}
old %>%
  rename(back_link=link_page) %>%
  rename(link_page=page) %>%
  rename(link_dir=dir) %>%
  select(link_dir, link_page, back_link, stub) -> mrg
new %>% 
  filter(link_miss==0) %>%
  filter(link_site=="www") %>%
  left_join(mrg, by=c("link_dir", "link_page")) %>%
  select(
    dir, 
    page, 
    link_dir, 
    link_page, 
    back_link,
    stub) -> pip1
pip1 %>%
  filter(is.na(stub)) %>%
    select(-stub) -> pip2 
msg <- glue(
  "{nrow(pip2)} / {n_new} = {round(100*nrow(pip2)/n_new)}%")
pip2 %>%
  mutate(dir=inc(dir)) %>%
  head(size_limit)
```

### pages with good links from new site to old site

```{r good-link-www}
pip1 %>%
  filter(!is.na(stub))  -> pip3 
glue("{nrow(pip3)} / {n_new} = {round(100*nrow(pip3)/n_new)}%")
pip3 %>%
  mutate(dir=inc(dir)) %>%
  head(size_limit)
```

### pages with no links from old site to new site

```{r no-link-new}
old %>% 
  filter(link_miss==1) %>%
  select(dir, page) -> pip1 
print(nrow(pip1))
pip1 %>%
  mutate(dir=inc(dir)) %>%
  head(size_limit)
```

### pages with bad links from old site to new site

```{r bad-link-new}
new %>%
  rename(back_link=link_page) %>%
  rename(link_page=page) %>%
  select(link_page, back_link, update) -> mrg

old %>%
  filter(link_miss==0) %>%
  left_join(mrg, by="link_page") %>%
  select(dir, page, link_page, update) -> pip1

pip1 %>%
  filter(is.na(update)) %>%
  select(-update)  -> pip4

print(nrow(pip4))
pip4 %>%
  mutate(dir=inc(dir)) %>%
  head(size_limit)
```

### pages with good links from old site to new site

```{r good-link-new}
pip1 %>%
  filter(!is.na(update)) -> pip5 
print(nrow(pip5))
pip5 %>%
  mutate(dir=inc(dir)) %>%
  head(size_limit)
```

### 2024-06-28 src/audit-old-pages.Rmd
Updated audit files

html_path <- paste(path1, path2, path3, sep="/")
subdir_list=c(
  "00",
  "00files",
  "01",
  "02",
  "03",
  "04",
  "05",
  "06",
  "07",
  "08",
  "08a",
  "09",
  "10",
  "11",
  "12",
  "12a",
  "13",
  "14",
  "15",
  "16",
  "17",
  "18",
  "99",
  "archive",
  "category",
  "definitions",
  "weblog",
  "08/accrual",
  "08/definitions",
  "08/diagnostic",
  "08/faq",
  "08/images",
  "08/journal",
  "08/koans",
  "08/software",
  "08/training",
  "08/training/abstracts",
  "08/training/datasets",
  "08/training/exercises",
  "08/training/extras",
  "08/training/images",
  "08/website")
save_file <- "../data/check_old.RData"
```

### create html

```{r create}
html <- NULL
for (yr in rev(subdir_list)) {
  file_path <- paste(html_path, yr, sep="/")
  file_path %>%
    list.files(pattern="asp|htm$|html$") -> piper
  if (length(piper) == 0) next
  piper %>%
    str_remove("\\..*") -> fn
  piper %>%
    str_remove(".*\\.") -> ext
  data.frame(yr=yr, fn=fn, ext=ext) %>%
    bind_rows(html) -> html
}
n <- nrow(html)
```

@@

```{r size}
search_size <- function(tx) {
  ty <- str_remove_all(tx, "\\s")
  length(tx)-sum(ty == "")
}
```

@@

```{r read}
# The str_trim function is not working. There
#  may be an encoding problem. See
#   "about_encoding" in the stringi package
#   https://search.r-project.org/CRAN/refmans/
#     stringi/html/about_encoding.html
#
# Help may come from the "stri_enc_toutf8" function 
#   https://search.r-project.org/CRAN/refmans/
#     stringi/html/stri_enc_toutf8.html
# A simpler solution may be
#   str_remove_all("\\s")
full_name <-
  paste0(
  html_path, "/",
  html$yr, "/",
  html$fn, ".",
  html$ext)
html$size <- -1
html$link <- "999"
for (i in 1:n) {
  tx <- read_lines(full_name[i])
  html$link[i] <- search_link(tx)
  html$size[i] <- search_size(tx)
}
html$miss <- as.numeric(nchar(html$link) == 0)
html$stub <- as.numeric(html$size <= 10)
html <- arrange(html, yr, fn)
save(html, file=save_file)
```

@@

```{r simple}
summary(html$size)
count(html, ext)
count(html, miss)
count(html, stub)
```

>>>>

old_path <- paste(path1, path2, path3, sep="/")
old_list=c(
  "00",
  "00files",
  "01",
  "02",
  "03",
  "04",
  "05",
  "06",
  "07",
  "08",
  "08a",
  "09",
  "10",
  "11",
  "12",
  "12a",
  "13",
  "14",
  "15",
  "16",
  "17",
  "18",
  "99",
  "archive",
  "category",
  "definitions",
  "weblog",
  "08/accrual",
  "08/definitions",
  "08/diagnostic",
  "08/faq",
  "08/images",
  "08/journal",
  "08/koans",
  "08/software",
  "08/training",
  "08/training/abstracts",
  "08/training/datasets",
  "08/training/exercises",
  "08/training/extras",
  "08/training/images",
  "08/website")
save_file <- "../data/check_old.RData"
```

### create old

```{r create}
old <- NULL
for (dir in rev(old_list)) {
  file_path <- paste(old_path, dir, sep="/")
  file_path %>%
    list.files(pattern="asp$|htm$|html$") -> piper
  if (length(piper) == 0) next
  piper %>%
    str_remove("\\..*") -> page
  piper %>%
    str_remove(".*\\.") -> ext
  data.frame(dir=dir, page=page, ext=ext) %>%
    bind_rows(old) -> old
}
rows <- nrow(old)
```

@@

```{r size}
# The str_trim function is not working. There
#  may be an encoding problem. See
#   "about_encoding" in the stringi package
#   https://search.r-project.org/CRAN/refmans/
#     stringi/html/about_encoding.html
#
# Help may come from the "stri_enc_toutf8" function 
#   https://search.r-project.org/CRAN/refmans/
#     stringi/html/stri_enc_toutf8.html
# A simpler solution may be
#   str_remove_all("\\s")

search_size <- function(tx) {
  ty <- str_remove_all(tx, "\\s")
  length(tx)-sum(ty == "")
}
```

@@

```{r read}
full_name <-
  paste0(
  old_path, "/",
  old$dir, "/",
  old$page, ".",
  old$ext)

old$size <- -1
old$link_page <- "999"

for (i in 1:rows) {
  tx <- read_lines(full_name[i])
  old$size[i] <- search_size(tx)
  old$link_page[i] <- search_link(tx)
}
```

```{r modify-variables}
old$stub <- as.numeric(old$size <= 10)
old$link_miss <- as.numeric(nchar(old$link_page) == 0)
```

```{r save}
old %>%
  select(
    dir, 
    page, 
    ext, 
    size,
    stub,
    link_miss,
    link_page) %>%
  arrange(dir, page) -> old

save(old, file=save_file)
```

@@

```{r simple}
summary(old$size)
count(old, ext)
count(old, link_miss)
count(old, stub)
```
